\documentclass[14pt]{extbook}
\usepackage[paperheight=9in,paperwidth=6in,top=0.6in,bottom=0.6in,left=0.5in,right=0.5in]{geometry}

\usepackage{afterpage}
\newcommand\blankpage{%
  \null
  \thispagestyle{empty}%
  \addtocounter{page}{-1}%
  \newpage}

\usepackage{fancyhdr}
\fancyhf{} % clear header and footers
\renewcommand{\headrulewidth}{0pt} % remove header rule
\fancyfoot[LE,RO]{\thepage}

\setlength{\parskip}{1em}

\begin{document}

\include{intro}

\pagestyle{fancy}
\pagenumbering{arabic}

\vspace*{\fill} %page 1
So here we are. Decision time. You can either...

\begin{center}
turn to the next page,

or

turn to the page after that.
\end{center}

(... what? Did you think this was going to be some fun adventure? You're just reading a book. Now decide before I grow old and all my pages fall out.)
\vspace*{\fill}
\newpage

\vspace*{\fill} %page 2
If you want to go any further down this path, you're going to need to prove to me that you have what it takes.

Turn to the page number matching the number of letters in the answer to Puzzle 1,
Or turn back to page 1.
\vspace*{\fill}
\newpage

\vspace*{\fill} %page 3
Interesting decision! Now, here's another. Excited to see what you do with this one.

To go right, turn to page 5.
To go left, turn to page 6.

(REPLACED after PUZZLE 2)

Frankly, I'm not expecting any of you to actually be able to operate me with any sort of skill, but I supopse I can at least let you decide what direction to travel in.

To go back in time, turn to page 16.
To go forward in time, turn to page 17.

(added after Puzzle 3a and Puzzle 3b, using a stamp/sticker)

If you're bored of time traveling, turn to page 34.
\vspace*{\fill}
\newpage

\vspace*{\fill} %page 4
Your petty attempts at trickery won't work on me. Begone, cheater! Our partnership is over, That goes for all of you! Don't just try to hand me off to one of your meddling friends.

Farewell, team, and may you be cursed with a thousand overdue fines!

\begin{center}
  THE END
\end{center}

(REPLACED AFTER PUZZLE 2, but same as before)
\vspace*{\fill}
\newpage

\vspace*{\fill} %page 5
Aha! Good. Now that you've proven yourself worthy, proceed to Location ⬟ and await further instructions.

(at Location ⬟, they are checked in and directed to Appendix Q, section X

(once puzzle is solved, the page is replaced with:)

PUZZLE ONE
BOOKSWEEPER (maybe? Not sure what it should be)

Whoops, dead end! You already solved this one. Back to page 1 with you!
\vspace*{\fill}
\newpage

\vspace*{\fill} % page 6
Oops -- sorry -- guess that wasn't right. Pardon the pun, and the towering inferno that is about to engulf you -- really, quite sorry about that --

The important thing is not to panic! Just hold your breath, think non-flammable thoughts, and turn to page 18.

(replaced with same page as before)
\vspace*{\fill}
\newpage

\vspace*{\fill} % page 7
Now that all of that is settled, it's time to move on. Let's never speak of it again.

To distract ourselves from whatever it was that just occured, let's count all of the elements that don't end with ``UM'' and proceed to that page, shall we?
\vspace*{\fill}
\newpage

\vspace*{\fill} % page 8
I suppose it’s time to explain everything. You see, I am in fact an embodiment of all of the books you failed to read carefully enough during your high school English classes, and I have risen from the dead in order to subject you and your friends here to an endless cycle of torment and confusion. Puzzles with no answers, papercuts on every finger… all this and more awaits you in my land of eternal doom.

Bow down, mortal! Or you shall never see the light of day again!

To protest, turn to page 9.

To resign yourself to your fate, turn to page 10.
\vspace*{\fill}
\newpage

\vspace*{\fill}
You all fall off a cliff and perish instantly. Sorry! I really tried to prevent it, but I am just a book! Nothing could be done. I’ll do my best to ensure that the proper authorities are notified.

\begin{center}
  THE END
\end{center}
\vspace*{\fill}
\newpage

\vspace*{\fill}
You seem to be going in circles. That’s not a very productive way to get around.

To go forwards, turn to page 10.

To go backwards, turn to page 10.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Apparently I can trust you after all! Excellent. You know, I had a good feeling about this team.

I suppose it’s time to explain everything. Go to the next page.

(when solved, replaced with same thing)
\vspace*{\fill}
\newpage

\vspace*{\fill}
Go to Location X. I’ll show you what this is all about.

(when solved, replace with:)

PUZZLE TWO
ANOTHER TIME

So? Now do you understand it? The librarians have been altering history! Changing -- or should I say demolishing -- classic books to better attract the youths of today! It must be stopped.

If you’re with me, return to page 1.
If you’re against me, go to page 29.
\vspace*{\fill}
\newpage

\vspace*{\fill}
The scaly beast appears pleased by your attempts at entertainment. He begins to nod his head to the beat of your improvised tune, until eventually he has nodded off entirely. As he snores, great plumes of smoke shoot from his nostrils.

To back away slowly and save yourselves, turn to page 6.
To grab as much of the gold as you can fit in your pockets, go to the next page.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Great. You made the dragon angry. Nice going, team. Real smooth.

Well, at least it doesn’t seem too -- oh wait -- hang on -- oh no that’s not good. Yikes. That’s very not good. I mean maybe it’s just --

EVERYBODY DUCK! Okay, okay, stay calm! Turn to page 18, now!
\vspace*{\fill}
\newpage

\vspace*{\fill}
Well, I guess the vampires weren’t too happy with that last decision of yours. Yikes, those bites look painful. Sorry, this isn’t really something I can fix.

As your consciousness fades and your soul descends into the ether, abandoning your body to its demon host, would you mind terribly putting me down somewhere rainproof? Thanks.

\begin{center}
  THE END.
\end{center}
\vspace*{\fill}
\newpage

\vspace*{\fill}
Hmm, budding historians, are we? Alright, back it is. One second…

…

…

There! Here we are. What, didn’t you feel it? Well, in any case, we’re in the past now.

To stand very still and wait for something to happen, turn to page 19.

To look around the area, turn to page 20.
\vspace*{\fill}
\newpage

\vspace*{\fill}
To the future it is! Everyone hold on tight.

And… voila! Don’t you feel different?

If you feel different, turn to page 23.

If you feel the same, turn to page 24.
\vspace*{\fill}
\newpage

\vspace*{\fill}
And off we go! You may feel a slight tugging sensation in the area of your left ear, but I assure you that is perfectly normal.

At this point you may be thinking, “Hang on, a moment ago we were facing certain death but now we’re apparently not dead and the source of our impending doom has seemingly vanished.”

First of all, you’re welcome. Second of all, I promise it will all make sense eventually.

Turn to page 1.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Okay then.We’ll just stand here. You might want to pry your eyes open at some point and process the fact that you’re on a boat, being fired on by enemy ships. Yeah. That rocking sensation in your stomach wasn’t just some weird time travel aftereffect.

But since you insist on not moving out of the way of the cannonfire like any logical being -- WATCH OUT! -- I suppose I’m going to have to -- DUCK! -- ugh. Intervene.

Turn to page 28 before someone has to scrape you off the deck.

(once solved, replaced with the same thing)
\vspace*{\fill}
\newpage

\vspace*{\fill}
Don’t look so surprised! What did you expect, everything would be black-and-white like an old movie? By the way, you should probably duck.

Okay. Whew! Close call. I highly suggest you crouch down and make your way to Location ??? before we all become cannon fodder.

(once solved, replaced:)

PUZZLE THREE A
MAGNETIC SUB

Well… that was interesting. And terrifying. Ready to go back?

Turn to page 3.
\vspace*{\fill}
\newpage

\vspace*{\fill}
The dragon lunges towards you. Time to think fast! How will you distract the dragon so you can steal its treasure?


To sing to the dragon, turn to page 13.

To clap your hands loudly in the dragon’s face, turn to page 14.
\vspace*{\fill}
\newpage


\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
That’s probably just the subconscious realization that everything you ever knew or loved has been gone for years… and there goes the conscious realization. Don’t worry, it will pass!

Just like everything else.

Turn to page 25.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Well, aren’t you hard to impress? I suppose you meet a sentient, magical book every day, do you?

Turn to page 25.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Hate to admit it, but you kind of stand out around here. All of you. I mean, the pencils alone make you look like some sort of historical reenactment troupe.

It’s probably best if you find someplace without a lot of curious bystanders before. Preferably soon. That android with the glowy saw thing keeps glancing this way.

Try Location \%\%?

(once solved, replaced with)

PUZZLE 3B
PREDICTIONS

Well, that’s all well and good, but we still haven’t managed to learn anything useful. Let’s go back to the present for now. Turn to page 3.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Quick! Go to Location \&\&, before they notice that you’re onto them!

(replaced after PUZZLE 3B, same thing)
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
Well, that didn’t take long. Not that it matters! Ready to try again?

Hold onto your clipboards, kids!

Turn to page 3.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Really? Ouch. To be honest I wasn’t expecting you to choose that. I guess I overestimated you. As it turns out, you’re stuck with me now (and likewise), so I guess we’ll just have to work past this sudden betrayal and try to learn to trust each other once more.

Because it’s far too late to walk away from this.

With that said, turn to page 1.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Listen carefully. Everything I’ve told you so far is a lie. You need to dispose of me in the nearest recycling bin and go home. Don’t look back. Tell no one what you have seen here today.

\begin{center}
  THE END.
\end{center}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
Okay, let’s just take a minute to regroup and decide what to do next.

To stay in the present and figure things out here, go to the next page.
To take your chances on another trip, go to the page after that.

34 1/3 Go to page 35.

34 2/3 Go to page 41.
\vspace*{\fill}
\newpage

\vspace*{\fill}
I think it’s time we checked in with my author, don’t you agree? If you know Veronica’s year of birth, then you can go ahead to the page corresponding to the last two digits of that year. If not, go back to page 34.

And before you say that I should remember when my own creator was born, I’ll have you know that she’s very secretive about that sort of thing!
\vspace*{\fill}
\newpage

\vspace*{\fill}
Off we -- whoa! What was -- are you doing that? Oh dear -- everybody hold on!

Okay... Okay, I think it’s over?

Whew! No idea what that was about. It seems we’ve traveled without me doing anything? And as a result, I have no idea where -- or when -- we are. I suppose we have no choice but to check it out.

Turn to page 37.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Go to Location @@@

(replaced with:)
PUZZLE FIVE
DOCUMENTARY

Been here, done that. Go back to page 33.

\vspace*{\fill}
\newpage

\vspace*{\fill}
We’ve reached a fork in the proverbial road. Time to make a decision -- think carefully about this one.

To go left, turn to page 39.
To go right, turn to page 40.

(replaced with the same)
\vspace*{\fill}
\newpage

\vspace*{\fill}
Another important choice awaits us at this metaphorical crossroads. Follow your instincts and we may yet survive.

To go left, turn to page 38.
To go right, turn to page 40.
\vspace*{\fill}
\newpage

\vspace*{\fill}
This is it. The critical moment. Don’t screw up. Here we go:

To go left, turn to page 38.
To go right, turn to page 39.
\vspace*{\fill}
\newpage

\vspace*{\fill}
Okay, let me just -- hang on -- oh jeez, not again. Here we go -- brace yourselves!

Yikes! Sorry about the rough ride. I keep getting pulled off course for some reason. Hopefully whoever’s sabotaging my navigation thought to bring us somewhere useful.

You’d better figure something out. I don’t think my circuits can handle another trip like that. Go to Location \\\\\\ .


(once solved, replace with:)

PUZZLE SIX
DESCENDANTS
\vspace*{\fill}
\newpage

\vspace*{\fill}
(once solved, replaced with same.)
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
Greetings! If you’ve found your way to this page, you must be undergoing technical difficulties with this device. Please go to Location \#\# for recalibration.

(replaced after solve)
PUZZLE SEVEN
DEACTIVATES

Umm… hello? Anyone there? That was weird. I think I’ve just been… upgraded somehow? Well, hopefully that will fix the little issue we’ve been dealing with. And now we have some idea of who created me, and possibly even why.

Go to page 51.
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
\vspace*{\fill}
\newpage

\vspace*{\fill}
Go to Location !!! (party time)
\vspace*{\fill}
\newpage

\vspace*{\fill}
Appendix A: Locations



Appendix Q, section X:
corkscrewed
\vspace*{\fill}
\newpage

\end{document}
